|

### 2025-01-26 doc/paper.qmd
final for now

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable  
**HU**: Humboldt-Universität zu Berlin  
**IV**: Independent Variable  
**EU**: European Union  ##  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom  ##  
**US**:: United States  
**WRDS**: Wharton Research Data Services

>>>>

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices  
**CQA**: Corporate Decision-Making and Quantitative Analysis  
**DV**: Dependent Variable  
**HU**: Humboldt-Universität zu Berlin  
**IDE**: Integrated Development Environment  
**IV**: Independent Variable  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**US**:: United States  
**WRDS**: Wharton Research Data Services
